**The status of the microbial census: an update**

### 2015-11-10 Schloss_Census2_mBio_2015.Rmd
Trying to get version numbers in citation parentheses

***Data analysis.***
Our analysis made use of ARB [OS X v.6.0, @Pruesse2007], mothur mothur [v.1.37.0; @Schloss2009], and R [v.`r paste(version$major, version$minor, sep='.')`; @language2015]. Within R we utilized knitr [v.`r packageDescription("knitr")$Version`; @xie2013dynamic] and openxlsx [v. `r packageDescription("openxlsx")$Version`; @Walker2015] packages. A reproducible version of this manuscript including data extraction and processing is available at https://www.github.com/SchlossLab/Schloss_Census2_mBio_2015.

@@

Issues we sought to solve...
* How have the number of full-length sequences changed over the past N years?
* How does this vary by environment?
* How has the coverage of the OTUs represented by these sequences changed over the last N years?
* How has the number of sequences per study changed over the past N years?
* How has Figure 1 changed over the past N years?

>>>>

***Data analysis.***
Our analysis made use of ARB (OS X v.6.0) [@Pruesse2007], mothur (v.1.37.0) [@Schloss2009], and R (v.`r paste(version$major, version$minor, sep='.')`) [@language2015]. Within R we utilized knitr (v.`r packageDescription("knitr")$Version`) [@xie2013dynamic] and openxlsx (v. `r packageDescription("openxlsx")$Version`) [@Walker2015] packages. A reproducible version of this manuscript including data extraction and processing is available at https://www.github.com/SchlossLab/Schloss_Census2_mBio_2015.

@@

Issues we sought to solve...

* How have the number of full-length sequences changed over the past N years?
* How does this vary by environment?
* How has the coverage of the OTUs represented by these sequences changed over the last N years?
* How has the number of sequences per study changed over the past N years?
* How has Figure 1 changed over the past N years?
